GravExplain: Continuous gravitational wave searches in a table-top experiment

### 2020-02-13 paper/paper_main.tex
small change in intro text

% continuous gws
To date the network of gravitational-wave observatories have observed short-duration transient signals~\cite{GWTC-1:2018,GWOSC:online}. 
These observatories are also searching for continuous gravitational waves (CW); persistent periodic signals at near-monochromatic frequencis. 
One of the prime targets of CW searches are rotating neutron stars in low mass X-ray binaries (LMXBs).
LMXBs are binary systms containing a compact object (such as a neturon star or a black hole) in orbit with a low mass stellar companion~\cite{xraybinaries:1997}. 
The LMXB Scorpius X-1 is an LMXB which is particularly bright in X-rays. 
It is a prime target for CW searches from LMXBs and numerous searches have been performed~\cite{2019PhRvD.100l2002A,RadiometerO1O2:2019,SearchCrossCorrO1:2017}.

>>>>

% continuous gws
To date the network of gravitational-wave observatories have observed short-duration transient signals~\cite{GWTC-1:2018,GWOSC:online}. 
These observatories are also searching for continuous gravitational waves; persistent periodic signals at near-monochromatic frequencis. 
One of the prime targets of continuous wave searches are rotating neutron stars in low mass X-ray binaries (LMXBs).
LMXBs are binary systms containing a compact object (such as a neturon star or a black hole) in orbit with a low mass stellar companion~\cite{xraybinaries:1997}. 
The LMXB Scorpius X-1 is an LMXB which is particularly bright in X-rays. 
It is a prime target for continuous wave searches from LMXBs and numerous searches have been performed~\cite{2019PhRvD.100l2002A,RadiometerO1O2:2019,SearchCrossCorrO1:2017}.
